A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-06-21 paper.Rmd
Added Ellis and Woo references

We discuss how to share and/or publish data and cover various tradeoffs when deciding how much to do. We skip detailed discussions of the minutiae of data preparation (TODO: We need to cite these articles), licenses (there are not many options when it comes to data), or citation (as of this writing, data citation is still in its infancy). We also analyze the state of data contained inside software packages, shared and made available as part of modern data analysis. How often are data shipped inside software packages? How does data format and size impact availability?

>>>>

We discuss how to share and/or publish data and cover various tradeoffs when deciding how much to do. We skip detailed discussions of the minutiae of data preparation [@Broman2017; @Ellis2017], or citation (as of this writing, data citation is still in its infancy). We also analyze the state of data contained inside software packages, shared and made available as part of modern data analysis. How often are data shipped inside software packages? How does data format and size impact availability?
